1-generate-toys

### 2018-06-27 scripts/3-metric_characterisation/1old-generate_toys.Rmd
reorganise dynalysis

## Generate toy datasets for comparing scores
```{r}
source("analysis/analyses/3-score_rules/generation.R")
source("analysis/analyses/3-score_rules/perturbation.R")

experiment("3-score_rules/1-generate_toys")
```

>>>>

## Generate toy datasets for comparing scores
```{r}
source("analysis/analyses/3-metric_characterisation/generation.R")
source("analysis/analyses/3-metric_characterisation/perturbation.R")

experiment("3-metric_characterisation/1-generate_toys")
```
